Do investors in clean energy ETFs herd?

### 2025-03-24 alt_energy_herding.qmd
finalising comments still

tribble(
  ~ "Variable", ~ "Coefficient",
  "lambda_0", " -1.506***",
  "lambda_1", "-4.607***",
  "lambda_2", "-1.318", 
  "Log Likelihood", "-484.7",
  "Observations with Dependent Variable (Dep) = 0", "1816",
  "Observations with Dependent Variable (Dep) = 1", "134"
) %>% 
  flextable_pdf() %>% 
  align(align = "left", j = 1, part = "all") %>%
  mk_par(j = 1, i = c(1, 2, 3), part = "body", value = as_paragraph(as_equation(lambda))) %>% 
  add_footer_lines(
    values = as_paragraph(
      "Notes: **,*** denotes statistically significant at 5% and 1%"
    )
  ) %>% 
  hline(part = "body", i = 3, border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  autofit(add_w = 1.5)

>>>>

tribble(
  ~ "Variable", ~ "Coefficient",
  "lambda_0", " -1.506***",
  "lambda_1", "-4.607***",
  "lambda_2", "-1.318", 
  "Log Likelihood", "-484.7",
  "Observations with Dependent Variable (Dep) = 0", "1816",
  "Observations with Dependent Variable (Dep) = 1", "134"
) %>% 
  flextable_pdf() %>% 
  align(align = "left", j = 1, part = "all") %>%
  mk_par(j = 1, i = c(1, 2, 3), part = "body", value = as_paragraph(as_equation(lambda))) %>% 
  add_footer_lines(
    values = as_paragraph(
      "Notes: **,*** denotes statistically significant at 5% and 1%"
    )
  ) %>% 
  hline(part = "body", i = 3, border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  autofit(add_w = 1.4)

### 2025-03-24 alt_energy_herding.tex
finalising comments still

\begin{longtable}[l]{|p{3.78in}|p{2.14in}}

@@

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Variable}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Coefficient}}}} \\

@@

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.506***}}}} \\

@@

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_1$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-4.607***}}}} \\

@@

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.318}}}} \\

@@

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Log\ Likelihood}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-484.7}}}} \\

@@

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Observations\ with\ Dependent\ Variable\ (Dep)\ =\ 0}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{1816}}}} \\

@@

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Observations\ with\ Dependent\ Variable\ (Dep)\ =\ 1}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{134}}}} \\

@@

\multicolumn{2}{>{\raggedright}m{\dimexpr 5.92in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Notes:\ **,***\ denotes\ statistically\ significant\ at\ 5\%\ and\ 1\%}}}} \\

>>>>

\begin{longtable}[l]{|p{3.68in}|p{2.04in}}

@@

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Variable}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Coefficient}}}} \\

@@

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.506***}}}} \\

@@

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_1$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-4.607***}}}} \\

@@

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.318}}}} \\

@@

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Log\ Likelihood}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-484.7}}}} \\

@@

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Observations\ with\ Dependent\ Variable\ (Dep)\ =\ 0}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{1816}}}} \\

@@

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Observations\ with\ Dependent\ Variable\ (Dep)\ =\ 1}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{134}}}} \\

@@

\multicolumn{2}{>{\raggedright}m{\dimexpr 5.72in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Notes:\ **,***\ denotes\ statistically\ significant\ at\ 5\%\ and\ 1\%}}}} \\
